Concordance between observations and simulations in the evolution of the mass relation between supermassive black holes and their host galaxies

### 2022-04-28 projects/2020_HSC_to_numerical_simulation/manuscript/manuscript.tex
resubmit for ApJ

%% The first piece of markup in an AASTeX v6.x document is the \documentclass
%% command. LaTeX will ignore any data that comes before this command. The 
%% documentclass can take an optional argument to modify the output style.
%% The command below calls the preprint style which will produce a tightly 
%% typeset, one-column, single-spaced document.  It is the default and thus
%% does not need to be explicitly stated.
%%
%% using aastex version 6.3
%\documentclass[twocolumn, linenumbers]{aastex631}
\documentclass[twocolumn]{aastex631}

\newcommand{\vdag}{(v)^\dagger}
\newcommand\aastex{AAS\TeX}
\newcommand\latex{La\TeX}
\newcommand{\todo}[1]{\textcolor{red}{[{\bf TODO}: #1]}}
\newcommand{\ding}[1]{\textcolor{red}{[{\bf Xuheng}: #1]}}
\newcommand{\jshi}[1]{\textcolor{orange}{#1}}
\newcommand{\blue}[1]{\textcolor{blue}{#1}}
\newcommand{\yo}[1]{\textcolor{purple}{[{\bf Yohan}: #1]}}
\newcommand{\red}[1]{\textcolor{purple}{#1}}

@@

\author[0000-0002-0000-6977]{John D.Silverman}
\affiliation{Kavli Institute for the Physics and Mathematics of the Universe, The University of Tokyo, Kashiwa, Japan 277-8583 (Kavli IPMU, WPI)}

@@

\begin{abstract}
We carry out a comparative analysis of the relation between the mass of supermassive black holes (BHs) and the stellar mass of their host \red{galaxies} at $0.2<z<1.7$ using well-matched observations and multiple state-of-the-art simulations (e.g., Massive Black II, Horizon-AGN, Illustris, TNG and a semi-analytic model). The observed sample consist of 646 uniformly-selected SDSS quasars ($0.2 < z < 0.8$) and 32 broad-line AGNs ($1.2<z<1.7$) with imaging from Hyper Suprime-Cam (HSC) for the former and Hubble Space Telescope (HST) for the latter. \red{We} first add realistic observational uncertainties to the simulation data and then construct a simulated sample in the same manner as the observations. Over the full redshift range, our analysis demonstrates that all simulations predict a level of intrinsic scatter of the scaling relations comparable to the observations which appear to agree with the dispersion of the local relation. Regarding the mean relation, Horizon-AGN and TNG are in closest agreement with the \red{observations} at low and high redshift ($z\sim$ 0.2 and 1.5, respectively) while the other simulations show subtle differences within the uncertainties. For insight into the physics involved, the scatter of the scaling relation, seen in the SAM, is reduced by a factor of two and closer to the observations after adopting a new feedback model which considers the geometry of the AGN outflow. The consistency in the dispersion with redshift in our analysis \red{supports} the importance of both quasar and radio mode feedback prescriptions in the simulations. Finally, we \red{highlight the importance of increasing} the sensitivity, e.g., JWST, thereby pushing to lower masses and minimizing biases \red{due to} selection effects.
\end{abstract}
\keywords{Galaxy evolution (594); Active galaxies (17); Active galactic nuclei (16)}

@@

The AGN feedback consists of three components, namely quasar-mode, radio-mode and radiative feedback. In the quasar-mode which holds for BHs with Eddington ratio $>0.01$, the AGNs deposit $5\%$~(quasar-mode feedback efficiency) of their released energy into the surrounding gas as thermal energy. For Eddington ratios $<0.01$, the AGN feedback is in radio-mode where the thermal energy is released as hot bubbles with a radius of $\sim$ 100~kpc at \red{the} intervals between which the BH mass grows by a fixed fraction. 
(%\todo{Aklant: Referee asks: are these irregular intervals included in the feedback modeling, or simply due to the time-varying accretion onto BHs? does it mean that the BH accretion is not modeled by the Bondi accretion between AGN feedback events?} \aklant{\bf{They are irregular simply because the BH mass growth is non- uniform. So it takes different amounts of time for the BH to grow by a fixed fraction. Bondi accretion is happening at all times. I have now removed the word `irregular' from this statement.}} 
The energy of the bubbles is given by $\epsilon_m \epsilon_r \delta M_{BH} c^2$ where $\delta M_{BH}$ is the change in BH mass within the last time interval, and $\epsilon_m=0.35$ is the radio-mode feedback efficiency. Lastly, the radiative feedback mode is implemented by modifying the heating and cooling rates of the gas in the presence of radiation from all surrounding AGN. \red{Halos and galaxies are identified similar to that of MBII}. As in MBII, a 3D 30~kpc spherical aperture is used to obtained the galaxy \red{stellar mass}. %, assuming a \cite{2003PASP..115..763C} IMF.

@@

%\todo{TNG100 and TNG300 -- explain the why no difference between TNGs. P8}~\red{We note that TNG100 and TNG300 yield very similar comparison results, thus only TNG100 is presented in~Figure~\ref{fig:comparsion}}.
\red{In the literature~\citep{Weinberger2018, Habouzit2021}, it has been noted that the mass correlations predicted by TNG300 and TNG100 are not identical. For example, TNG300 appares to have different scatter in \mbh\ at fixed \smass\ to TNG100 at \smass $>10^{10}M_{\odot}$. Also, BH growth is more efficient in TNG100 thus causing the BH mass function to have higher normalization at the low mass end. In our work, the differences between TNG100 and TNG300 also exist. However, the difference are milder after selection effects and random noise injection have been applied to the samples.} \todo{The referee says TNG300 has larger scatter, but in Habouzit2021 section 4.2.2, it actually says scatter in TNG300 is smaller. Any one know if the referee is wrong?}

@@

\item{} Regarding the \red{offsets of the scaling relation from the local one} ($\Delta$\mbh\ at a given \smass; D20), {\it all simulations generally match the observations} with some subtle, yet notable, differences. While Illustris\red{, MBII,} and Horizon-AGN show good correspondence with observations at $z<0.6$, the comparisons at $z>0.6$ are better for SAM, \red{MBII,} TNG100, TNG300 and Horizon-AGN. Bridging the gap from \hbox{$z\sim0.7$} to $z\sim1.5$, TNG100, TNG300 and Horizon-AGN simulations match well the observed evolution of the scaling relation, i.e., the offsets are larger at higher redshift as shown in Figure~\ref{fig:offsets_vz} and Table~\ref{tab:sum}. Four out of six of the simulations have a decreasing mass offset from $z=0.2$ to $z=0.6$ while the observational mass offset increases with redshift; however, this is well below the observed scatter.
\end{enumerate}

@@

\bibliography{reference}{}
%\input{manuscript.bbl}
\bibliographystyle{aasjournal}

>>>>

%% The first piece of markup in an AASTeX v6.x document is the \documentclass
%% command. LaTeX will ignore any data that comes before this command. The 
%% documentclass can take an optional argument to modify the output style.
%% The command below calls the preprint style which will produce a tightly 
%% typeset, one-column, single-spaced document.  It is the default and thus
%% does not need to be explicitly stated.
%%
%% using aastex version 6.3
\documentclass[twocolumn, linenumbers]{aastex631}
%\documentclass[twocolumn]{aastex631}

\newcommand{\vdag}{(v)^\dagger}
\newcommand\aastex{AAS\TeX}
\newcommand\latex{La\TeX}
\newcommand{\todo}[1]{\textcolor{red}{[{\bf TODO}: #1]}}
\newcommand{\jshi}[1]{\textcolor{orange}{#1}}
\newcommand{\blue}[1]{\textcolor{blue}{#1}}
%\newcommand{\red}[1]{\textcolor{purple}{#1}}
\newcommand{\red}[1]{{\bf #1}}

@@

\author[0000-0002-0000-6977]{John D. Silverman}
\affiliation{Kavli Institute for the Physics and Mathematics of the Universe, The University of Tokyo, Kashiwa, Japan 277-8583 (Kavli IPMU, WPI)}

@@

\begin{abstract}
We carry out a comparative analysis of the relation between the mass of supermassive black holes (BHs) and the stellar mass of their host \red{galaxies} at $0.2<z<1.7$ using well-matched observations and multiple state-of-the-art simulations (e.g., Massive Black II, Horizon-AGN, Illustris, TNG and a semi-analytic model). The observed sample consist\red{s} of 646 uniformly-selected SDSS quasars ($0.2 < z < 0.8$) and 32 broad-line AGNs ($1.2<z<1.7$) with imaging from Hyper Suprime-Cam (HSC) for the former and Hubble Space Telescope (HST) for the latter. \red{We} first add realistic observational uncertainties to the simulation data and then construct a simulated sample in the same manner as the observations. Over the full redshift range, our analysis demonstrates that all simulations predict a level of intrinsic scatter of the scaling relations comparable to the observations which appear to agree with the dispersion of the local relation. Regarding the mean relation, Horizon-AGN and TNG are in closest agreement with the \red{observations} at low and high redshift ($z\sim$ 0.2 and 1.5, respectively) while the other simulations show subtle differences within the uncertainties. For insight into the physics involved, the scatter of the scaling relation, seen in the SAM, is reduced by a factor of two and closer to the observations after adopting a new feedback model which considers the geometry of the AGN outflow. The consistency in the dispersion with redshift in our analysis \red{supports} the importance of both quasar and radio mode feedback prescriptions in the simulations. Finally, we \red{highlight the importance of increasing} the sensitivity, e.g., JWST, thereby pushing to lower masses and minimizing biases \red{due to} selection effects.
\end{abstract}
\keywords{Galaxy evolution (594); Active galaxies (17); Active galactic nuclei (16)}

@@

The AGN feedback consists of three components, namely quasar-mode, radio-mode and radiative feedback. In the quasar-mode which holds for BHs with Eddington ratio $>0.01$, the AGNs deposit $5\%$~(quasar-mode feedback efficiency) of their released energy into the surrounding gas as thermal energy. For Eddington ratios $<0.01$, the AGN feedback is in radio-mode where the thermal energy is released as hot bubbles with a radius of $\sim$ 100~kpc at \red{the} intervals between which the BH mass grows by a fixed fraction. 
%\todo{Aklant: Referee asks: are these irregular intervals included in the feedback modeling, or simply due to the time-varying accretion onto BHs? does it mean that the BH accretion is not modeled by the Bondi accretion between AGN feedback events?} \aklant{\bf{They are irregular simply because the BH mass growth is non- uniform. So it takes different amounts of time for the BH to grow by a fixed fraction. Bondi accretion is happening at all times. I have now removed the word `irregular' from this statement.}} 
The energy of the bubbles is given by $\epsilon_m \epsilon_r \delta M_{BH} c^2$ where $\delta M_{BH}$ is the change in BH mass within the last time interval, and $\epsilon_m=0.35$ is the radio-mode feedback efficiency. Lastly, the radiative feedback mode is implemented by modifying the heating and cooling rates of the gas in the presence of radiation from all surrounding AGN. \red{Halos and galaxies are identified similar to that of MBII}. As in MBII, a 3D 30~kpc spherical aperture is used to obtained the galaxy \red{stellar mass}. %, assuming a \cite{2003PASP..115..763C} IMF.

@@

%\todo{TNG100 and TNG300 -- explain the why no difference between TNGs. P8}~\red{We note that TNG100 and TNG300 yield very similar comparison results, thus only TNG100 is presented in~Figure~\ref{fig:comparsion}}.
\red{In the literature~\citep{Weinberger2018, Habouzit2021}, it has been noted that the mass correlations predicted by TNG300 and TNG100 are not identical. For example, TNG300 appares to have different scatter in \mbh\ at fixed \smass\ to TNG100 at \smass $>10^{10}M_{\odot}$. Also, BH growth is more efficient in TNG100 thus causing the BH mass function to have higher normalization at the low mass end. In our work, the differences between TNG100 and TNG300 also exist. However, the difference are milder after selection effects and random noise injection have been applied to the samples.} 
%\todo{The referee says TNG300 has larger scatter, but in Habouzit2021 section 4.2.2, it actually says scatter in TNG300 is smaller. Any one know if the referee is wrong?}

@@

\item{} Regarding the \red{offsets of the scaling relation from the local one} ($\Delta$\mbh\ at a given \smass; D20), {\it all simulations generally match the observations} with some subtle, yet notable, differences. While Illustris\red{, MBII,} and Horizon-AGN show good correspondence with observations at $z<0.6$, the comparisons at $z>0.6$ are better for SAM, \red{MBII,} TNG100, TNG300 and Horizon-AGN. Bridging the gap from \hbox{$z\sim0.7$} to $z\sim1.5$, TNG100, TNG300 and Horizon-AGN simulations match well the observed evolution of the scaling relation, i.e., the offsets are larger at higher redshift as shown in Figure~\ref{fig:offsets_vz} and Table~\ref{tab:sum}. \red{Four out of six of the simulations have a decreasing mass offset from $z=0.2$ to $z=0.6$ while the observational mass offset increases with redshift; however, this is well below the observed scatter.}
\end{enumerate}

@@

%\bibliography{reference}{}
\input{manuscript.bbl}
\bibliographystyle{aasjournal}
